---
title: "Partnerships_draft_code"
author: "Annabelle"
date: "July 14, 2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Set up file structure 
```{r, include = FALSE}
## setup the file structure so that this markdown document is in the main project folder along with the other folders noted below

DataSource <- "./data" # input raw dataset goes here
output.dir <-"./output" # output dataset writes to here
functions.dir <- "./functions" # directory for functions 

source(file.path(functions.dir,'FormatData.R')) # any functions that are called up by this markdown document need to be sourced here
source(file.path(functions.dir,'cleaning_salafsky.R')) # any functions that are called up by this markdown document need to be sourced here
source(file.path(functions.dir,'FormatwCollabs.R')) # any functions that are called up by this markdown document need to be sourced here
source(file.path(functions.dir,'salafsky_final_edits.R')) # any functions that are called up by this markdown document need to be sourced here
source(file.path(functions.dir,'multipartnerstrings.R')) # any functions that are called up by this markdown document need to be sourced here

## general functions that need to be read in. I like to put them at the top so they are easier to deal with when they change version (inevitable)
library(plyr) #for function "join_all" also note, there can be issue loading this after dplyr (which is why it's at the top)
library(readr)
library(readxl)
library(tidyverse)
library(dplyr)
library(janitor) #used in cleaning 
library(stringr)
library(car) #for function qqplot 
library(knitr) #for making tables form kable 
library(data.table) #function setnames() allows to set multiple column names in one line of code 
library(igraph)
```

##load in different datasets
```{r, echo = FALSE, include = FALSE}
CleanData <- read.csv(paste0(DataSource,"/codesalafsky.csv"), stringsAsFactors = FALSE) #removing end piece  ## codesalafsky.csv is the rawest data that function runs on
code <- cleaning_salafsky(CleanData)
sdata <- read_csv(paste(DataSource,"/tableofpartnersandactions.csv", sep = "")) #this csv is produced at end of cleaning_salafsky.R function 
#sdata <- sdata %>% select(-X1) #remove X1 column that is getting produced 

tdata <- read.csv(paste0(DataSource,"/Updated_variables.csv"), stringsAsFactors = FALSE) #data provided by tyler 
tdata <- tdata %>%  as_tibble() #now can use stringr packages 
tdata <- tdata %>%  ##cleaning/reformating colunm names --> default is lower_case_snake
                  clean_names()
##

tableofPandA <- read.csv(paste0("/usr/local/bin/store/partner_rff/data/tableofPandAmodified.csv"), stringsAsFactors = FALSE, na = "", #issue was that "" is coming up instead of NA
               strip.white=TRUE)
## New csv made for changes made as final cleaning steps (replacing partner strings that were "all" with relevant partner names)
modPA <- salafsky_final_edits(tableofPandA)
docspef <- multipartnerstrings(modPA)

PartnersDataModified <- read.csv(paste0("/usr/local/bin/store/partner_rff/data/PartnersDataModified.csv"), 
                                stringsAsFactors = FALSE, na = c("", " ", "NA"))
newpdata <- FormatwCollabs(PartnersDataModified)


##orgtyp_base <- read.csv(paste0("/usr/local/bin/store/partner_rff/data/tableofPandAmodified.csv"), stringsAsFactors = FALSE, na = "") #issue was that "" is coming up instead of NA
## file name got changed

orgtype <- orgtyp_base ## taken from Data_exploration script 
```



#### Number of species 
```{r}
# number count 
pcount <- newpdata[-c(91,92),]
pcount <- pcount[-which(is.na(pcount$partner_names)),]
dim(pcount) ##52 

# salafsky counts 
docspef <- as.data.frame(docspef)
count(unique(docspef$Scientific.name)) ##37
```


#### Number of partners
##### Larger df 
```{r}
FedAg_w_collab <- pcount[,c(1,2,5)]

EditedData <- FedAg_w_collab

for (i in 1:nrow(EditedData)) {
  dvec <- trimws(strsplit(EditedData$FedAg_w_collab[i],split=",")[[1]])
  for (dname in dvec) {
    if (dname%in%colnames(EditedData)) {
      EditedData[i, dname] <- 1              
    } else {
      EditedData[dname] <- 0
      EditedData[i, dname] <- 1                                    
    }
  }
}

dim(EditedData) #294 - 3(first three columns in df) = 291 - this is different because now includes Fed Agency offices and what were previously collaborators
```


##### Larger df 
```{r}

count(unique(docspef$partner.in.agreement)) #140 
## still have 3 groups issues to take care of 

```





Other to do from doc 

put number of actions into the number of partners regression?
- this was done in Codeforoverviewdoc w actpartsum and action sum 


Is there a subset of this for which we can identify the identity of the partners? If so, how many are there?


Historgram of Taxa - what are the NAs??



This section has some confusion I think because of M vs noM counts. I think we should report the M counts here in all cases. Needs to be fixed.



Number of partners per species 



Can we say something about a “general” suite of actions and how the compliment of actions is achieved by the partnership?











### Checking to see which partners are all 0s 




